Demes: a standard format for demographic models

### 2022-08-10 paper.tex
Basic changes for Genetics

\documentclass[11pt]{article}
\usepackage[round,comma,authoryear]{natbib}
\usepackage{fullpage}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage[labelformat=simple]{subcaption}

@@

% Import this last to avoid mysterious errors.
\usepackage[implicit=false]{hyperref}

@@

\newcommand{\aprcomment}[1]{{\textcolor{blue}{APR: #1}}}
\newcommand{\jkcomment}[1]{{\textcolor{red}{JK: #1}}}
\newcommand{\ggcomment}[1]{{\textcolor{yellow!60!red}{GG: #1}}}
\newcommand{\krtcomment}[1]{{\textcolor{purple}{KRT: #1}}}
\newcommand{\mhcomment}[1]{{\textcolor{cyan}{MH: #1}}}

@@

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Gertjan Bisschop}
\author[4]{Ryan N. Gutenkunst}
\author[3]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[8]{Stephan Schiffels}
\author[4]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\aleph$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

@@

\affil[$\star$]{Denotes shared first authorship, listed alphabetically}
\affil[$\dagger$]{Denotes shared senior authorship, listed alphabetically}
\affil[$\aleph$]{Denotes corresponding author}

\maketitle

@@

\section*{Introduction}

@@

\bibliographystyle{genetics}
\bibliography{paper}

>>>>

\documentclass[9pt,twocolumn,twoside]{gsajnl}
\articletype{inv} % article type

\usepackage{booktabs}
\usepackage{amsmath}
\usepackage[labelformat=simple]{subcaption}

@@

% Import this last to avoid mysterious errors.
% \usepackage[implicit=false]{hyperref}

@@

@@

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Gertjan Bisschop}
\author[4]{Ryan N. Gutenkunst}
\author[3]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[8]{Stephan Schiffels}
\author[4]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\ddagger$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

@@

% \affil[$\star$]{Denotes shared first authorship, listed alphabetically}
% \affil[$\dagger$]{Denotes shared senior authorship, listed alphabetically}
% \affil[$\aleph$]{Denotes corresponding author}

\keywords{Demographic models, inference, simulation}

\runningtitle{Demes: a standard format for demographic models}
\runningauthor{Gower \textit{et al.}}

@@

\maketitle
\thispagestyle{firststyle}
\marginmark
\firstpagefootnote

% Use the \equalcontrib command to mark authors with equal
% contributions, using the relevant superscript numbers
% \equalcontrib{1}
% \equalcontrib{2}
\makeatletter
\newcommand{\equalcontribfirst}[1]{\@authfootnote{#1}{These authors contributed equally to this work, as joint first authors.}}
\newcommand{\equalcontriblast}[1]{\@authfootnote{#1}{These authors contributed equally to this work, as joint last authors.}}
\makeatother

\equalcontribfirst{$\star$} % {Denotes shared first authorship, listed alphabetically}
\equalcontriblast{$\dagger$} % {Denotes shared senior authorship, listed alphabetically}
% \equalcontrib{$\ddagger$}{Denotes corresponding author}

\correspondingauthoraffiliation{$\ddagger$}{\url{jerome.kelleher@bdi.ox.ac.uk}}
\vspace{-33pt}% Only used for adjusting extra space in the left column of the first page
\section*{Introduction}

@@

% \bibliographystyle{genetics}
\bibliography{paper}
